Re-run, Repeat, Reproduce, Re-use, Replicate:\\Transforming Code into Scientific Contributions

### 2017-07-03 main.tex
Layout change

Replicability is a cornerstone of science.
If an experimental result cannot be re-obtained by an independent party,
% it might be because of a fluke, a bias, a bug, a false positive or even a hack.
%it becomes, at best, nothing more than food for thought for future research. 
it merely becomes, at best, an observation that
may feed future research (\cite{Mesirov:2010,osc:2015}). 
Replication issues have received increased attention in recent years,
in the domain of medicine and psychology in particular (\cite{Iqbal:2016}).

One could think that computer science would mostly be shielded from such issues.
But precisely because it is easy to believe that
if a program runs once and gives expected results it will do so forever, 
crucial steps to transform working code into meaningful scientific contributions are rarely undertaken \citep{Sandve:2013,Schwab:2000}. 
Computer science is plagued by replication problems,
in part, precisely because it seems impervious to them.

In fact, a program can fail as a scientific contribution
in many different ways for many different reasons.
Borrowing the terms coined by \citeauthor{Goble:2016} \citep{Goble:2016},
for your program to contribute to Science,
you have to make sure it is
re-runnable (R$^1$),
repeatable (R$^2$),
reproducible (R$^3$),
re-usable (R$^4$)
and replicable (R$^5$).

@@

% -------------------------
\clearpage
\section*{Re-runnable (R$^{\mathbf 1}$)}

Have you ever try to re-run a program you wrote some years ago?
Frustratingly, it can often be surprisingly hard. 
Part of the problem is that technology is evolving at a fast pace
and you cannot  know in advance
how the system, the software and the libraries your program depends on will evolve.
Since you wrote the code,
you may have reinstalled or upgraded  your operating system.
The compiler, interpreter or set of libraries installed may have been replaced with newer versions. 
You may find yourself battling with
arcane issues of library compatibility---thoroughly orthogonal to your immediate research  goals---to execute again a code \emph{that worked perfectly before}. 
% "thoroughly orthogonal to your immediate research goals": possibly problematic

To be clear, it is impossible to write future-proof code,
and the best efforts can be stymied by the smallest change in one of the dependencies.
At the same time, modernizing an unmaintained ten-year-old code
can reveal itself to be an arduous and expensive undertaking,
with each change risking to affect the semantics of the program.

Rather trying to predict the future or painstakingly dusting off old code, 
an often easier and less dangerous solution is to recreate the old execution environment.
For this to happen however, 
the dependencies in terms of systems, software and libraries must be made clear enough.

@@

In our case, the R$^0$ version of our tiny walker seems to imply
that any version of Python would be fine.
This not the case because it uses the print {\em instruction} and the {\tt xrange} operator, both specific to Python 2.
The print {\em instruction}, available in Python 2 (a version still widely used; support is scheduled to stop in 2020), 
has been deprecated in Python 3 (first released in 2008, almost a decade ago)
in favor or a  print {\em function}.
The {\tt xrange} operator has been replaced by the {\tt range} operator in Python 3.
In order to try to future-proof the code a bit, we might as well target Python 3, as is done in the R$^1$ version.
Incidentally, it remains compatible with Python 2.

But whatever version is chosen,
the crucial step here is to document it.

@@

The code is running and producing the expected results. 
The next step is to make sure that you can produce the same output over successive runs of your program. 
In other words, the next step is to make your program deterministic,  producing {\em repeatable} output. 
Such repeatability is useful. 
If a run of the program produces a particularly puzzling results,  it allows you to scrutinize any step of the execution of the program by re-running it again with extraneous prints, or inside a debugger. 
It is also the easiest way to prove that the program did indeed produce the published results.
Such repeatability is not always possible or easy \citep{Diethelm:2012, Courtes:2015}.
But for sequential programs not depending on exotic hardware, it often comes down to controlling the initialization of the pseudo-random number generators (RNG).\\

For our program, that means setting the seed of the {\tt random} module. We may also want to save the output of the program to a file, so that we can easily verify that consecutive runs do produce the same output: eyeballing differences is unreliable and  time-consuming---and therefore won't be done systematically.

@@

Setting seeds is not without danger. 
Using 439 as a seed in the previous program would result in ten consecutive +1 steps, which---although a perfectly valid random walk---lend itself to a gross misinterpretation of the overall dynamic of the algorithm. 
Verifying that the qualitative aspects of the results and the conclusion we make are not tied to a specific initialization of the pseudo-random generator is an integral part of any scientific undertaking in computational science; 
this is usually done by repeating the simulations multiple times with different seeds.

%Determinism is a tool that allow to study bugs and spurious or unexpected behavior. 
%Determinism is also critical for other to reproduce and study your results. 
% talk about controversy about setting seeds

% For example, you can play with some parameters and
% find a specific set that produce interesting results that you save to a file.
% In the meantime, you continue playing with parameters in order get new results.
% But what if you want to come back to this one specific result you just saved?
% Did you save as well the set of parameters tied to this specific results? 
% This kind of situation happens quite regularly in the scientific literature \cite{Claerbout:2000} 
% such that in some case, it is virtually impossible
% to find the set of parameters that has been used to produce this or that figure.
% If you're note careful enough, this will happen to you as well.\\

@@

As explained by \citeauthor{Mesnard:2016} \citep{Mesnard:2016}, reproducibility is hard. 
For instance, the R$^2$ program will not produce the same results all the time. It will, because it is repeatable, produce the same results over repeated executions.
But it will not do so over different execution environments. The cause is found in a change that occurred in the pseudo-random number generator between Python 3.2 and Python 3.3. 
Executed with Python 2.7 to 3.2, the code will produce the sequence 1, 2, 1, 2, 3, 4, 5, 6, 7, 6. But with Python 3.3 to 3.6, it will produce 1, 2, 1, 0, 1, 0, 1, 0, -1, 0.\\

% Reproducible definition + R^2 not reproducible
Because any dependency of your program---to the most basic one, the language itself---can change its behavior from one version to another, executability (R$^1$) and determinism (R$^2$) are necessary but not sufficient for reproducibility. The exact execution environment used to produce the results must also be specified---rather than the broadest set of environments where the code can be executed. In other words, assertions such as "the results were obtained with Python 3.6.1" are more valuable, in a scientific context, than "the program should work with Python 3.3.x and above".\\

% Reproducibility is hard
Because of the increasing complexity of our computational stacks, retrieving and deciding what is pertinent (CPU architecture? Operating system version? Endianness?) might be difficult.
See Appendix \ref{appendix:executionenvs} for a discussion.\\

% Reproducibility in practice.
Having precisely described the execution environment, reproducibility is technically obtained. However, \emph{reproducibility in practice} requires more than that.

% Saving Parameters
The R$^2$ program uses a random seed but does not keep a trace of it except in the code. Therefore, should the code change after the production of the results, someone provided with the result file will not be able to know which seed was used, and would need to iterate through all possible random seeds, which is not possible in practice. R$^3$ saves the seed in the name of the result file. More generally, results should always come alongside their context, i.e. an exhaustive list of the parameters used and a description of the execution environment.\\

% Data behind graphs
Graphs in articles are powerful way to communicate complex information. They are imprecise and cumbersome, and sometimes plain unusable, however when it comes to checking that the reproduced data match the one published in the article. A good figure should always be accompanied by its underlying data to allow straightforward comparisons.\\

% Unit test for R^3
Another good practice is to make the code self-verifiable. In R$^3$, a short unit test is provided, that allows the code to verify its own reproducibility. Should this test fail, then there is little hope of reproducing the results. Of course, passing the test is no definitive proof.\\

% Reproducibility implies availability 
It should be obvious by now but \emph{reproducibility implies availability}. As shown in \citep{Collberg:2016}, code is often unavailable, or only available upon request. While the latter may seem sufficient, changes in email address, changes in career, retirement, a busy inbox or poor archiving practices can make a code just as unreachable. Code \emph{and input and result files} should be available with the published article, as supplementary data, or through a DOI link to a scientific repository such as Figshare or Zenodo\footnote{Online code repository such as GitHub \emph{are not} scientific repositories, and may disappear, change name, etc. at any moment. Direct links to them are not perpetual and should be avoided.}.\\

%\begin{itemize}
%\itemsep 0em
%\item Python 3
%\item Python 3.6
%\item {Python 3.6.1 (default, Mar 28 2017, 10:33:50) \\
%      {\tt [GCC 4.2.1 Compatible Apple LLVM 8.1.0 (clang-802.0.38)] on darwin}}
%\item {Python 3.6.1 (default, Mar 28 2017, 10:33:50) \\
%      {\tt [GCC 4.2.1 Compatible Apple LLVM 8.1.0 (clang-802.0.38)] on darwin}\\
%      {\tt configuration variables: -std=c99 -Wextra -Wno-unused-result -Wno-unused-parameter -Wno-missing-field-initializers ...}}
%\end{itemize}

@@

\clearpage
\section*{Re-usable (R$^{\mathbf 4}$)}

Making your program re-usable means it can be easily used, and modified, by you and other people, inside and outside your lab. Ensuring your program is re-usable is advantageous for a number of reasons.\\

For you, first. Because the you now and the you in two years are two different persons. Details on how to use the code, its limitations, its quirks, may be present to your mind now, but will probably escape you in six months \parencite{Donoho:2009}. Here, comments and documentation can make a significant difference.\\

Furthermore, a source code reflects the results of all the decisions that were made to create it, but not the reasons behind them. In science, where the method and its justification matters as much as the results, those reasons are precious knowledge. For instance, it is not sufficient to observe that a piece of code is doing correct predictions on a learning task, one is interested by the exact algorithm that is employed, and why. In that context, a comment on how a given parameter was chosen (optimization, experimental data, educated guess, …) is a valuable information.\\

Re-usability of course directly benefits others researchers, from your team and outside of it. The easier it is to use your code, the lower is the threshold for other to study, modify and extend it. Scientists constantly face the constraint of time: if a model is available, documented, and can be installed, run and understood all in a few hours, it will be preferred over another that would require weeks to reach the same stage.\\

Moreover, scientists prefer to base their work on results they can verify. A reproducible and re-usable code offers a platform both verified and easy-to-use, fostering the development of derivative works by other researchers. Those derivative works contribute to the impact of your original contribution, and generate citations.\\

Having more people examining and using your code also means that potential errors have a higher chance to be caught. If people start using your program, they will most likely report bugs or malfunctions they encountered while using your program. If you're lucky enough, they might even propose you either bugfixes or improvements, hence improving the overall quality of your software. This process contributes to the long-term reproducibility to the extent people continue to use and maintain the program.

% * <fabien.benureau+overleaf@gmail.com> 2017-06-16T09:22:07.537Z:
% 
% I'd like to refactor this section into:
% 1. Why re-usability is important for you (you will be stranger to yourself in six month)
% 2. Why it is important for others (1. they will be more likely to cite your work, 2. long-term reproducibility)
% 3. Tips and general guidelines on how to do it.
% 
% ^.

However, making your program to be re-usable by others requires a little work. If it is natural, when one writes a program for oneself, to make implicit choices that suit one needs, such implicit choices won't resist the will of a user community. For example, having magic numbers or ill-defined constants in your program might be cumbersome for others. Similarly, it might be acceptable to not have a proper documentation when you're the only user (actually it might not be acceptable because the you now and the you in six months are two different persons), but other users want to know precisely how to use this or that function and what it does exactly.\\

If we look back at our random walker, we can list all the implicit choices that have been made:
\begin{itemize}
\item Step number has been hard-coded (magic number 10)
\item Step size has been fixed to 1
\item Initial position has been set to 0
\item No possibility of using a user-specified random seed
\item Only one run can be started at once
\item Walker walk along a single dimension
\item ...
\end{itemize}
However, we won't try to implement all these features at once, but only giving the possibility for a user to implement them if needed.

@@

In our case, the replication of the random walk brings some unexpected discrepancies between the original Python version and the replicated Numpy version.
The reason is to be found in a differences in the respective implementations of the RNG between Python and Numpy.
As explained in the \href{https://docs.python.org/3.6/library/random.html}{Python documentation}, {\em Python uses the Mersenne Twister as the core generator. It produces 53-bit precision floats
and has a period of 2**19937-1.
The underlying implementation in C is both fast and threadsafe.}
Numpy RNG is also based on the Mersenne Twister generator but there are differences in the way seed is interpreted when initializing the generator.
Fortunately, Both Numpy and Python offer access to the internal state and we can {\em fix} it to make the behavior of one RNG to match the other RNG.
Here, we want to make the Numpy RNG to match the Python RNG behavior.\\

Without such explicit replication effort, it would be very hard to discover this faulty behavior and this why the ReScience journal has been created.
This journal targets computational research and encourages the explicit replication of already published research, promoting new and open-source implementations in order to ensure that the original research is reproducible.

@@

\newpage 
\appendix

\section{Appendix: Recording Execution Environments}
\label{appendix:executionenvs}
Talk about provenance-tracking and its problems (endianess, "as well as any defaults you may have set that might have an impact.")

Talk about saving VMs, Docker images and its problems.

>>>>

Replicability is a cornerstone of science.  If an experimental result cannot be
re-obtained by an independent party, it merely becomes, at best, an observation
that may feed future research (\cite{Mesirov:2010,osc:2015}).  Replication
issues have received increased attention in recent years, in the domain of
medicine and psychology in particular (\cite{Iqbal:2016}). One could think that
computer science would mostly be shielded from such issues.  But precisely
because it is easy to believe that if a program runs once and gives expected
results it will do so forever, crucial steps to transform working code into
meaningful scientific contributions are rarely undertaken
\citep{Sandve:2013,Schwab:2000}.  Computer science is plagued by replication
problems, in part, precisely because it seems impervious to them.
In fact, a program can fail as a scientific contribution in many different ways
for many different reasons.  Borrowing the terms coined by
\citeauthor{Goble:2016} \citep{Goble:2016}, for your program to contribute to
Science, you have to make sure it is re-runnable (R$^1$), repeatable (R$^2$),
reproducible (R$^3$), re-usable (R$^4$) and replicable (R$^5$).

@@

% -------------------------
% \clearpage
\section*{Re-runnable (R$^{\mathbf 1}$)}

Have you ever try to re-run a program you wrote some years ago?  Frustratingly,
it can often be surprisingly hard.  Part of the problem is that technology is
evolving at a fast pace and you cannot know in advance how the system, the
software and the libraries your program depends on will evolve.  Since you
wrote the code, you may have reinstalled or upgraded your operating system.
The compiler, interpreter or set of libraries installed may have been replaced
with newer versions.  You may find yourself battling with arcane issues of
library compatibility---thoroughly orthogonal to your immediate research
goals---to execute again a code \emph{that worked perfectly before}.  To be
clear, it is impossible to write future-proof code, and the best efforts can be
stymied by the smallest change in one of the dependencies.  At the same time,
modernizing an unmaintained ten-year-old code can reveal itself to be an
arduous and expensive undertaking, with each change risking to affect the
semantics of the program. Rather than trying to predict the future or painstakingly
dusting off old code, an often easier and less dangerous solution is to
recreate the old execution environment.  For this to happen however, the
dependencies in terms of systems, software and libraries must be made clear
enough.

@@

In our case, the R$^0$ version of our tiny walker seems to imply that any
version of Python would be fine.  This not the case because it uses the print
{\em instruction} and the {\tt xrange} operator, both specific to Python 2.
The print {\em instruction}, available in Python 2 (a version still widely
used; support is scheduled to stop in 2020), has been deprecated in Python 3
(first released in 2008, almost a decade ago) in favor or a print {\em
  function}.  The {\tt xrange} operator has been replaced by the {\tt range}
operator in Python 3.  In order to try to future-proof the code a bit, we might
as well target Python 3, as is done in the R$^1$ version.  Incidentally, it
remains compatible with Python 2. But whatever version is chosen, the crucial
step here is to document it.

@@

The code is running and producing the expected results.  The next step is to
make sure that you can produce the same output over successive runs of your
program.  In other words, the next step is to make your program deterministic,
producing {\em repeatable} output.  Such repeatability is useful.  If a run of
the program produces a particularly puzzling results, it allows you to
scrutinize any step of the execution of the program by re-running it again with
extraneous prints, or inside a debugger.  It is also the easiest way to prove
that the program did indeed produce the published results.  Such repeatability
is not always possible or easy \citep{Diethelm:2012, Courtes:2015}.  But for
sequential programs not depending on exotic hardware, it often comes down to
controlling the initialization of the pseudo-random number generators (RNG).
For our program, that means setting the seed of the {\tt random} module. We may
also want to save the output of the program to a file, so that we can easily
verify that consecutive runs do produce the same output: eyeballing differences
is unreliable and time-consuming---and therefore won't be done systematically.

@@

Setting seeds is not without danger.  Using 439 as a seed in the previous
program would result in ten consecutive +1 steps, which---although a perfectly
valid random walk---lend itself to a gross misinterpretation of the overall
dynamic of the algorithm.  Verifying that the qualitative aspects of the
results and the conclusion we make are not tied to a specific initialization of
the pseudo-random generator is an integral part of any scientific undertaking
in computational science; this is usually done by repeating the simulations
multiple times with different seeds.
%Determinism is a tool that allow to study bugs and spurious or unexpected behavior. 
%Determinism is also critical for other to reproduce and study your results. 
% talk about controversy about setting seeds
% For example, you can play with some parameters and
% find a specific set that produce interesting results that you save to a file.
% In the meantime, you continue playing with parameters in order get new results.
% But what if you want to come back to this one specific result you just saved?
% Did you save as well the set of parameters tied to this specific results? 
% This kind of situation happens quite regularly in the scientific literature \cite{Claerbout:2000} 
% such that in some case, it is virtually impossible
% to find the set of parameters that has been used to produce this or that figure.
% If you're note careful enough, this will happen to you as well.\\

@@

As explained by \citeauthor{Mesnard:2016} \citep{Mesnard:2016}, reproducibility
is hard.  For instance, the R$^2$ program will not produce the same results all
the time. It will, because it is repeatable, produce the same results over
repeated executions.  But it will not do so over different execution
environments. The cause is found in a change that occurred in the pseudo-random
number generator between Python 3.2 and Python 3.3.  Executed with Python 2.7
to 3.2, the code will produce the sequence 1, 2, 1, 2, 3, 4, 5, 6, 7, 6. But
with Python 3.3 to 3.6, it will produce 1, 2, 1, 0, 1, 0, 1, 0, -1, 0.
% Reproducible definition + R^2 not reproducible
Because any dependency of your program---to the most basic one, the language
itself---can change its behavior from one version to another, executability
(R$^1$) and determinism (R$^2$) are necessary but not sufficient for
reproducibility. The exact execution environment used to produce the results
must also be specified---rather than the broadest set of environments where the
code can be executed. In other words, assertions such as "the results were
obtained with Python 3.6.1" are more valuable, in a scientific context, than
"the program should work with Python 3.3.x and above".
% Reproducibility is hard
Because of the increasing complexity of our computational stacks, retrieving
and deciding what is pertinent (CPU architecture? Operating system version?
Endianness?) might be difficult.  See Appendix \ref{appendix:executionenvs} for
a discussion.
% Reproducibility in practice.
Having precisely described the execution environment, reproducibility is technically obtained. However, \emph{reproducibility in practice} requires more than that.
% Saving Parameters
The R$^2$ program uses a random seed but does not keep a trace of it except in
the code. Therefore, should the code change after the production of the
results, someone provided with the result file will not be able to know which
seed was used, and would need to iterate through all possible random seeds,
which is not possible in practice. R$^3$ saves the seed in the name of the
result file. More generally, results should always come alongside their
context, i.e. an exhaustive list of the parameters used and a description of
the execution environment.
% Data behind graphs
Graphs in articles are powerful way to communicate complex information. They
are imprecise and cumbersome, and sometimes plain unusable, however when it
comes to checking that the reproduced data match the one published in the
article. A good figure should always be accompanied by its underlying data to
allow straightforward comparisons.
% Unit test for R^3
Another good practice is to make the code self-verifiable. In R$^3$, a short
unit test is provided, that allows the code to verify its own
reproducibility. Should this test fail, then there is little hope of
reproducing the results. Of course, passing the test is no definitive proof.\\

% Reproducibility implies availability 
It should be obvious by now but let us state it very explicitely:
\emph{reproducibility implies availability}. As shown in \citep{Collberg:2016},
code is often unavailable, or only available upon request. While the latter may
seem sufficient, changes in email address, changes in career, retirement, a
busy inbox or poor archiving practices can make a code just as
unreachable. Code \emph{and input and result files} should be available with
the published article, as supplementary data, or through a DOI link to a
scientific repository such as Figshare or Zenodo\footnote{Online code
  repository such as GitHub \emph{are not} scientific repositories, and may
  disappear, change name, etc. at any moment. Direct links to them are not
  perpetual and should be avoided.}.
%\begin{itemize}
%\itemsep 0em
%\item Python 3
%\item Python 3.6
%\item {Python 3.6.1 (default, Mar 28 2017, 10:33:50) \\
%      {\tt [GCC 4.2.1 Compatible Apple LLVM 8.1.0 (clang-802.0.38)] on darwin}}
%\item {Python 3.6.1 (default, Mar 28 2017, 10:33:50) \\
%      {\tt [GCC 4.2.1 Compatible Apple LLVM 8.1.0 (clang-802.0.38)] on darwin}\\
%      {\tt configuration variables: -std=c99 -Wextra -Wno-unused-result -Wno-unused-parameter -Wno-missing-field-initializers ...}}
%\end{itemize}

@@

% \clearpage
\section*{Re-usable (R$^{\mathbf 4}$)}

Making your program re-usable means it can be easily used, and modified, by you
and other people, inside and outside your lab. Ensuring your program is
re-usable is advantageous for a number of reasons. For you, first. Because the
you now and the you in two years (or two months in some cases) are two
different persons. Details on how to use the code, its limitations, its quirks,
may be present to your mind now, but will probably escape you in six months
\parencite{Donoho:2009}. Here, comments and documentation can make a
significant difference.  Furthermore, a source code reflects the results of all
the decisions that were made to create it, but not the reasons behind them. In
science, where the method and its justification matters as much as the results,
those reasons are precious knowledge. For instance, it is not sufficient to
observe that a piece of code is doing correct predictions on a learning task,
one is interested by the exact algorithm that is employed, and why. In that
context, a comment on how a given parameter was chosen (optimization,
experimental data, educated guess, …) is a valuable information.
%
Re-usability of course directly benefits others researchers, from your team and
outside of it. The easier it is to use your code, the lower is the threshold
for other to study, modify and extend it. Scientists constantly face the
constraint of time: if a model is available, documented, and can be installed,
run and understood all in a few hours, it will be preferred over another that
would require weeks to reach the same stage.  Moreover, scientists prefer to
base their work on results they can verify. A reproducible and re-usable code
offers a platform both verified and easy-to-use, fostering the development of
derivative works by other researchers.\\

Those derivative works contribute to the impact of your original contribution,
and generate citations. Having more people examining and using your code also
means that potential errors have a higher chance to be caught. If people start
using your program, they will most likely report bugs or malfunctions they
encountered while using your program. If you're lucky enough, they might even
propose you either bugfixes or improvements, hence improving the overall
quality of your software. This process contributes to the long-term
reproducibility to the extent people continue to use and maintain the program.
%
However, making your program to be re-usable by others requires a little
work. If it is natural, when one writes a program for oneself, to make implicit
choices that suit one needs, such implicit choices won't resist the will of a
user community. For example, having magic numbers or ill-defined constants in
your program might be cumbersome for others. Similarly, it might be acceptable
to not have a proper documentation when you're the only user (actually it might
not be acceptable because the you now and the you in six months are two
different persons), but other users want to know precisely how to use this or
that function and what it does exactly.
%
If we look back at our random walker, we can list all the implicit choices that
have been made:
\begin{itemize}
\item Step number has been hard-coded (magic number 10)
\item Step size has been fixed to 1
\item Initial position has been set to 0
\item No possibility of using a user-specified random seed
\item Only one run can be started at once
\item Walker walk along a single dimension
\item etc.
\end{itemize}
However, we won't try to implement all these features at once, but only giving the possibility for a user to implement them if needed.

@@

In our case, the replication of the random walk brings some unexpected
discrepancies between the original Python version and the replicated Numpy
version.  The reason is to be found in a differences in the respective
implementations of the RNG between Python and Numpy.  As explained in the
\href{https://docs.python.org/3.6/library/random.html}{Python documentation},
     {\em Python uses the Mersenne Twister as the core generator. It produces
      53-bit precision floats and has a period of 2**19937-1.  The underlying
       implementation in C is both fast and threadsafe.}  Numpy RNG is also
     based on the Mersenne Twister generator but there are differences in the
     way seed is interpreted when initializing the generator.  Fortunately,
     Both Numpy and Python offer access to the internal state and we can {\em
       fix} it to make the behavior of one RNG to match the other RNG.  Here,
     we want to make the Numpy RNG to match the Python RNG behavior.
%
Without such explicit replication effort, it would be very hard to discover
this faulty behavior and this why the ReScience journal has been created.  This
journal targets computational research and encourages the explicit replication
of already published research, promoting new and open-source implementations in
order to ensure that the original research is reproducible.

@@

\newpage 
\appendix
\section{Appendix: Recording Execution Environments}
\label{appendix:executionenvs}
%% Talk about provenance-tracking and its problems (endianess, "as well as any defaults you may have set that might have an impact.")

%% Talk about saving VMs, Docker images and its problems.
